Simultaneous Elicitation of Scoring Rule and Agent Preferences for Robust Winner Determination

### 2021-01-08 minimax.tex
fix leg figure2

%%% Load required packages here (note that many are included already).
\input{preamble/packages}
\input{preamble/math}
%for appendix
\usepackage{import}
\usepackage{algorithm, algpseudocode}
\usepackage{booktabs}
\usepackage{pgfplots}
\pgfplotsset{compat=1.17}

@@

			\addlegendimage{mark=triangle*,teal,mark size=2}
			\addlegendimage{mark=*,violet,mark size=2}
			\addlegendimage{mark=square*,green,mark size=2}
			\addlegendimage{mark=diamond*,red,mark size=2}
			\addlegendimage{mark=halfsquare right*,brown,mark size=2}
			\addlegendimage{mark=oplus*,blue,mark size=2}
			\addlegendimage{mark=pentagon*,cyan,mark size=2}
			\addlegendimage{mark=halfsquare left*,pink,mark size=2}
			\addlegendimage{mark=halfsquare*,magenta,mark size=2}

			\addplot[thick, mark=triangle*, mark size = {2}, mark indices = {35}, teal] table [x=k, y=5.10]{data/linearity.dat};
			\addlegendentry{m=5, n=10}
			\addplot[thick, mark=*, mark size = {2}, mark indices = {45}, violet] table [x=k, y=5.15]{data/linearity.dat};
			\addlegendentry{m=5, n=15}
			\addplot[thick, mark=square*, mark size = {2}, mark indices = {90}, green] table [x=k, y=5.20]{data/linearity.dat};
			\addlegendentry{m=5, n=20}
			\addplot[thick, mark=diamond*, mark size = {2}, mark indices = {150}, red] table [x=k, y=10.20]{data/linearity.dat};
			\addlegendentry{m=10, n=20}
			\addplot[thick, mark=oplus*, mark size = {2}, mark indices = {60}, blue] table [x=k, y=14.9]{data/linearity.dat};
			\addlegendentry{m=14, n=9}
			\addplot[thick, mark=halfsquare right*, mark size = {2}, mark indices = {60}, brown] table [x=k, y=skate]{data/linearity.dat};
			\addlegendentry{skate m14n9}
			\addplot[thick, mark=pentagon*, mark size = {2}, mark indices = {300}, cyan] table [x=k, y=10.30]{data/linearity.dat};
			\addlegendentry{m=10, n=30}
			\addplot[thick, mark=halfsquare left*, mark size = {2}, mark indices = {200}, pink] table [x=k, y=sushi]{data/linearity.dat};
			\addlegendentry{sushi m10n30}
			\addplot[thick, mark=halfsquare*, mark size = {2}, mark indices = {400}, magenta] table [x=k, y=15.30]{data/linearity.dat};
			\addlegendentry{m=15, n=30}

>>>>

%%% Load required packages here (note that many are included already).
\input{preamble/packages}
\input{preamble/math}
%for appendix
\usepackage{import}
\usepackage{algorithm, algpseudocode}
\usepackage{booktabs}
\usepackage{pgfplots}
%\pgfplotsset{compat=1.17}

@@

			\addlegendimage{mark=triangle*,teal,mark size=2}
			\addlegendimage{mark=*,violet,mark size=2}
			\addlegendimage{mark=square*,green,mark size=2}
			\addlegendimage{mark=diamond*,red,mark size=2}
			\addlegendimage{mark=halfsquare left*,blue,mark size=2}
			\addlegendimage{mark=halfsquare right*,brown,mark size=2}
			\addlegendimage{mark=pentagon*,cyan,mark size=2}
			\addlegendimage{mark=halfsquare*,magenta,mark size=2}

			\addplot[thick, mark=triangle*, mark size = {2}, mark indices = {35}, teal] table [x=k, y=5.10]{data/linearity.dat};
			\addlegendentry{m=5, n=10}
			\addplot[thick, mark=*, mark size = {2}, mark indices = {45}, violet] table [x=k, y=5.15]{data/linearity.dat};
			\addlegendentry{m=5, n=15}
			\addplot[thick, mark=square*, mark size = {2}, mark indices = {90}, green] table [x=k, y=5.20]{data/linearity.dat};
			\addlegendentry{m=5, n=20}
			\addplot[thick, mark=diamond*, mark size = {2}, mark indices = {150}, red] table [x=k, y=10.20]{data/linearity.dat};
			\addlegendentry{m=10, n=20}
			\addplot[thick, mark=halfquare left*, mark size = {2}, mark indices = {60}, blue] table [x=k, y=14.9]{data/linearity.dat};
			\addlegendentry{m=14, n=9}
			\addplot[thick, mark=halfsquare right*, mark size = {2}, mark indices = {60}, brown] table [x=k, y=skate]{data/linearity.dat};
			\addlegendentry{skate m14n9}
			\addplot[thick, mark=pentagon*, mark size = {2}, mark indices = {300}, cyan] table [x=k, y=10.30]{data/linearity.dat};
			\addlegendentry{m=10, n=30}
			\addplot[thick, mark=halfsquare*, mark size = {2}, mark indices = {400}, magenta] table [x=k, y=15.30]{data/linearity.dat};
			\addlegendentry{m=15, n=30}
